Capstone Movielens Report

### 2025-11-23 reports/capstone-movielens.site/02.5.UME-model.Rmd
OMR, UE, UME models: review.
Description refining: UME Model.

Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.

@@

  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *5-Fold Cross-Validation* samples;

  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.

  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.

>>>>

@@

  1. **Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples;

  2. **Fine-tuning:** Figuring out the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* of the model.

  3. **Retraining:** Retraining the model with the best value of $\lambda$ determined in the previous step.
